---
title       : Miles per Gallon Prediction
subtitle    : Developing Data Products - Course Project, Shiny Application and Reproducible Pitch
author      : Tamas Izsak
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Fuel consumption / efficiency

Most customers are very sensitive regarding the fuel consumption / efficiency of the new cars. Usually the reasons are:

- rising fuel price
- environmental awareness

The car manufacturers working hard to predict and lowering the cars fuel consumption. There are lot of factors witch can effect the fuel efficiency (including but not limited to):

- number of cylinders
- gross horsepower
- weight
- engine displacement
- rear axle ratio
- transmission type

--- .class #id 

## Using the mtcars dataset

The ```mtcars``` dataset can be used to build a model to show the effects of car 
characteristics on fuel efficiency. 

Dataset example:

```{r, results='asis', echo=FALSE}
data(mtcars);
library(xtable)
print(xtable(mtcars[1:8,]), type = "html")
```

--- .class #id 

## Modelling predictor contribution

Using a linear model, I determined the effect of gross horsepower, number of 
cylinders, and weight on fuel efficiency (mpg), and used this model to create a
function to predict fuel efficiency based on these factors.

```{r}
modelFit <- lm(mpg ~ hp + cyl + wt, data=mtcars)
modelFit$coefficients

mpg <- function(hp, cyl, wt) {
    modelFit$coefficients[1] + modelFit$coefficients[2] * hp + 
        modelFit$coefficients[3] * cyl + modelFit$coefficients[4] * wt
}
```

--- .class #id

## Miles per Gallon Prediction Shiny App

The Miles per Gallon Prediction Shiny App is available here:

https://tamasizsak.shinyapps.io/course_final/

- The user can input predictor values in the left sidebar.
- The fuel efficiency predictions shown in the main frame.
- The plots below the main content show how MPG compares with data from the mtcars dataset.